\section{Testing Environment and Method}
The automated tests were executed on 20 June 2026 with Node.js 22.12.0 using the built-in Node test runner and experimental coverage instrumentation. The command was:

\begin{Verbatim}[fontsize=\small,frame=single]
node --test --experimental-test-coverage \
  test/focusMetrics.test.js test/firestoreModels.test.js
\end{Verbatim}

The two suites focus on deterministic business logic that can be validated without external services. \texttt{focusMetrics.test.js} covers time formatting, invalid-value clamping, daily and total statistics, progress limits, session payloads, ISO date normalization, and elapsed-minute calculation. \texttt{firestoreModels.test.js} covers snapshot mapping, profile and session payloads, participant defaults, room normalization, active-room filtering, and rejection of unavailable rooms.

\section{Results}
All 18 test cases passed. No tests were skipped or cancelled. The observed test-runner duration was 144.99 ms in the final verification run.

\begin{table}[H]
\centering
\begin{tabular}{|l|r|}
\hline
\textbf{Metric} & \textbf{Result} \\ \hline
Test files & 2 \\ \hline
Test cases & 18 \\ \hline
Passed & 18 \\ \hline
Failed & 0 \\ \hline
Skipped / cancelled & 0 \\ \hline
Pass rate & 100\% \\ \hline
\end{tabular}
\caption{Automated test results}
\label{tab:test_results}
\end{table}

\section{Coverage}
\begin{table}[H]
\centering
\begin{tabular}{|l|r|r|r|}
\hline
\textbf{Source file} & \textbf{Lines} & \textbf{Branches} & \textbf{Functions} \\ \hline
\texttt{firestoreModels.js} & 100.00\% & 93.75\% & 100.00\% \\ \hline
\texttt{focusMetrics.js} & 100.00\% & 82.35\% & 100.00\% \\ \hline
\end{tabular}
\caption{Coverage of tested production modules}
\label{tab:coverage}
\end{table}

The results provide strong evidence for the extracted mapping and calculation functions, but they do not establish end-to-end correctness of the distributed application. Authentication providers, Firestore transactions and rules, camera permissions, token issuance, WebRTC connections, reconnection behavior, and UI interaction remain outside the automated suite.

\section{Recommended Validation Campaign}
The next validation layer should use the Firebase Emulator Suite to exercise authorization rules and concurrent room transactions. Integration tests should mock token-server failures and verify cancellation when the video view closes. Device testing should cover camera denial, backgrounding, network handover, LiveKit reconnection, and mixed web/native participants. Finally, end-to-end flows should verify that focus and room sessions appear correctly in the Dashboard on a second device.
